\documentclass{beamer}

\usecolortheme[light]{solarized}

\beamertemplatenavigationsymbolsempty

\begin{document}

    \begin{frame}
        1. On which island was Napoleon born?

        Answer: Corsica
    \end{frame}

    \begin{frame}
        2. Which city became capital of West-Germany in 1949?

        Answer: Bonn
    \end{frame}

    \begin{frame}
        3. Which lost city in South America was discovered in 1911 by the
        archaeologist Hiram Bingham?

        Answer: Machu Picchu
    \end{frame}

    \begin{frame}
        4. How long did Neil Armstrong’s first ever walk on the moon last: 20
        minutes, 2 hours or 20 hours?

        Answer: 2 hours
    \end{frame}

    \begin{frame}
        5. The Canadian Captain Arthur 'Roy' Brown is credited with bringing
        which man down?

        Answer: The Red Baron
    \end{frame}

    \begin{frame}
        6. Which Apollo 11 astronaut did not set foot on the moon?

        Answer: Michael Collins
    \end{frame}

    \begin{frame}
        7. What was the capital city of Portugal between the years 1808 and
        1821?

        Answer: Rio de Janeiro
    \end{frame}

    \begin{frame}
        8. Which country's flag, the oldest existing flag in the world,
        apparently fell out of the heavens during a battle on 15th June, 1219?

        Answer: Denmark (The Dannebrog)
    \end{frame}

    \begin{frame}
        9.  Which company owned most of what is now called Canada in the early
        colonial days?

        Answer: The Hudson Bay Company.
    \end{frame}

    \begin{frame}
        10. In what American state did the Wright brothers make the first
        successful powered flight by Man?

        Answer: North Carolina
    \end{frame}

\end{document}
