\documentclass{beamer}

\usecolortheme[light]{solarized}

\beamertemplatenavigationsymbolsempty

\begin{document}

    \begin{frame}
        1. Who won the 2017 FA Cup Final? 

        Answer: Arsenal
    \end{frame}

    \begin{frame}
        2. Which city was Britain's `City of Culture' for 2017?

        Answer: Hull
    \end{frame}

    \begin{frame}
        3. On what date was Donald Trump sworn in as president of the United
        States of America?

        Answer: January 20th 2017
    \end{frame}

    \begin{frame}
        4. Who won the Super Bowl in 2017?

        Answer: The New England Patriots
    \end{frame}

    \begin{frame}
        5. What did SpaceX do for the first time in 2017?

        Answer: first reflight of an orbital class rocket
    \end{frame}

    \begin{frame}
        6. In 2017, Netflix released a new Star Trek series: how many Star Trek
        series have their been?

        Answer: 6 (Original, Next Gen, DS9, Voyager, Enterprise, Discovery)
    \end{frame}

    \begin{frame}
        7. What did the Australian Bureau of Statistics release on the 15th of
        November 2017?

        Answer: Australian Marriage Law Postal Survey (61\% Yes)
    \end{frame}

    \begin{frame}
        8. What was the name of the winner of Eurovision 2017?

        Answer: Salvador Sobral
    \end{frame}

    \begin{frame}
        9. What is the name of the TV show Prince Harry's fiancee starred in?

        Answer: Suits
    \end{frame}

    \begin{frame}
        10. Which island of the British Commonwealth was most heavily damaged
        during Hurricane Maria?

        Answer: Dominica
    \end{frame}

\end{document}
