\documentclass{article}

\usepackage{multicol}
\usepackage{minted}
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}

\begin{document}

\begin{center}
    List the name of the programming language.
\end{center}


\begin{multicols}{2}

1.
\begin{minted}{R}
cat("Hello world\n")
\end{minted}

\columnbreak

\begin{flushright}
    Answer: R
\end{flushright}

\end{multicols}


\hrulefill
\begin{multicols}{2}

2.
\begin{minted}{rust}
fn main() {
    println!("Hello, world!");
}
\end{minted}

\columnbreak

\begin{flushright}
    Answer: Rust
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


3.
\begin{minted}{css}
body:before {
    content: "Hello World";
}
\end{minted}

\columnbreak

\begin{flushright}
    Answer: css
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}

4.
\begin{minted}{python}
print "Hello World"
\end{minted}

\columnbreak

\begin{flushright}
    Answer: Python 2
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


5.
\begin{minted}{brainfuck}
++++++++++[>+++++++>++++++++++>+++<<<-]>++.>+.+++++++
..+++.>++.<<+++++++++++++++.>.+++.------.--------.>+.
\end{minted}

\columnbreak

\begin{flushright}
    Answer: Brainf***
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


6.
\begin{minted}{cobol}
*****************************
IDENTIFICATION DIVISION.
PROGRAM-ID. HELLO.
ENVIRONMENT DIVISION.
DATA DIVISION.
PROCEDURE DIVISION.
MAIN SECTION.
DISPLAY "Hello World!"
STOP RUN.
****************************
\end{minted}

\columnbreak

\begin{flushright}
    Answer: COBOL
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


7.
\begin{minted}{basic}
Private Sub Workbook_Open()
    MsgBox "Hello world!"
End Sub
\end{minted}

\columnbreak

\begin{flushright}
    Answer: VBA for Excel
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


8.
\begin{minted}{sas}
* Writes as output title;
TITLE "Hello World!";
* writes to the log;
data _null_;
    PUT "Hello world!";
run;
\end{minted}

\columnbreak

\begin{flushright}
    Answer: SAS
\end{flushright}

\end{multicols}

\hrulefill
\begin{multicols}{2}


9.
\begin{minted}{python}
TITLE 'Hello World'.
\end{minted}

\columnbreak

\begin{flushright}
    Answer: SPSS
\end{flushright}

\end{multicols}


\hrulefill
\begin{multicols}{2}


10.
\begin{minted}{c}
#include <iostream>
using namespace std;

int main() 
{
    cout << "Hello, World!";
    return 0;
}
\end{minted}

\columnbreak

\begin{flushright}
    Answer: C++
\end{flushright}

\end{multicols}

\end{document}
